Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations

### 2021-09-13 doc/main_jfm.tex
update conclusion

>>>>

The single JP vesicle simulations end with obtaining JP bilayer stretching 
modulus $K_A$ and hydraulic permeability constant $P$. We extract these 
physical quantities from the Laplace pressure relationship that $R\Delta P$ is 
proportional to JP bilayer stretch. We describe the aqueous flux in membrane 
using a differential equation~\ref{eq:perm} and solve for the theoretical 
permeability constant $P$. In spite of producing these values with some discrepancy
using the default parameter set, we provide a new framework in measuring coarse-grained 
membrane permeability.
